Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-03-19 paper.Rmd
Update dissemination section

For the further dissemination of the tutorials a website has been launced^[https://ABMArchaeologists.github.io/ABMA_Website/#/]. The tutorials can be found on this website and there is a link that can be used for feedback. Additionally, the website contains: basic explanations of agent-based modelling, a recording from one of the workshops, videos from an online course at Leiden University [@spoc2019] and external resources people can use to learn agent-based modelling.

Github

>>>>

The tutorials are publically hosted on GitHub ^[https://ABMArchaeologists.github.io/ABMA_Website/#/]. Anyone interested can download the tutorials and their source code. To increase the accessibility and visibility of the tutorials, a website has been launced^[https://ABMArchaeologists.github.io/ABMA_Website/#/]. On this website, the tutorials can be followed without the need to download any software.

Besides, the tutorial, the website provides: a link that can be used for feedback, basic explanations of agent-based modelling, an introductory presentation from one of the workshops, videos from an online course at Leiden University [@spoc2019] and external resources people can use to learn agent-based modelling.
